\begin{thebibliography}{99}

\small


\bibitem{SCICO}
{\em Boulytchev D.} Combinators and Type-driven Transformers in
Objective Caml // Sci. Comput. Program. 2015.  v. 114. no. C. pp. 57–73.

%\bibitem{brooks}
%{\em Brooks Jr. F. P.}  The Mythical Man-month (Anniversary
%Ed.). — Boston, MA, USA : Addison-Wesley Longman Publishing Co.,
%Inc., 1995. — ISBN: 0-201-83595-9.

\bibitem{SYBOCaml}
{\em Boulytchev D., Mechtaev S.} Efficiently Scrapping Boilerplate
Code in OCaml // Workshop on ML. — ML ’11. — Tokyo, Japan, 2011.

\bibitem{InstantGenerics}
{\em Chakravarty M. M. T., Ditu G., Leshchinskiy R.} In\-stant Generics : Fast and Easy. — 2009.

\bibitem{HC}
{\em Filli\^atre J.-C., Conchon S.} Type-safe Modular Hashconsing // Workshop on ML. — ML ’06. — New York, NY, USA : ACM, 2006. — P. 12–19.

\bibitem{PolyVar}
{\em  Garrigue J.} Programming with Polymorphic Variants // Workshop on ML. — 1998.

\bibitem{PolyVarReuse}
{\em Garrigue J.} Code reuse through polymorphic variants // In
Workshop on Foundations of Software Engineering. — 2000.

\bibitem{CalculatingFP}
{\em  Gibbons J.} Calculating Functional Programs // Algebraic and
Coalgebraic Methods in the Mathematics of Program Construction:
International Summer School and Workshop Oxford, UK, April 10–14, 2000 Revised Lectures / Ed. by Roland Backhouse, Roy Crole,
Jeremy Gibbons. — Berlin, Heidelberg : Springer Berlin Heidelberg,
2002. — P. 151–203. %— ISBN: 978-3-540-47797-6. 
%— Access mode: https://doi.org/10.1007/3-540-47797-7_5.

\bibitem{DGP}
{\em Gibbons J.} Datatype-generic Programming // Proceedings
of the 2006 International Conference on Datatype-generic Program\-ming. — SSDGP’06. — Berlin, Heidelberg : Springer-Verlag, 2007. —
P. 1–71.% — 
%Access mode: http://dl.acm.org/citation.cfm?id=1782894.1782895.

\bibitem{Hinze}
{\em Hinze R.} Generics for the Masses // J. Funct. Program. — 2006. —
Jul. — Vol. 16, no. 4-5. — P. 451–483.
%Access mode: http://dx.doi.org/10.1017/S0956796806006022.

\bibitem{Fold}
{\em Hutton G.} A Tutorial on the Universality and Expressive\-ness of Fold // J. Funct. Program. — 1999. — Jul. — Vol. 9,
no. 4. — P. 355–372. %— Access mode: http://dx.doi.org/10.1017/S0956796899003500.

\bibitem{TypeFamilies}
{\em Kiselyov O., Jones S.P.,  Chung-chieh S. } Fun with
Type Functions // Reflections on the Work of C.A.R. Hoare / Ed. by
A.W. Roscoe, Cliff B. Jones, Kenneth R. Wood. — London : Springer
London, 2010. — P. 301–331. %— ISBN: 978-1-84882-912-1. 
%— Access mode: https://doi.org/10.1007/978-1-84882-912-1_14.

\bibitem{AGKnuth}
{\em Knuth D.E.} Semantics of context-free languages // Mathemati\-cal systems theory. — 1968. — Jun. — Vol. 2, no. 2. — P. 127–145. 
%— Access mode: https://doi.org/10.1007/BF01692511.

\bibitem{deBruijn}
{\em de Bruijn, N. G.} Lambda Calculus Notation with Nameless Dummies: A Tool for Automatic Formula Manipulation, with Application to the Church-Rosser Theorem. - 1972


\bibitem{OCanren}
{\em Kosarev D, Boulytchev D.} Typed Embedding of a Relational Language in OCaml // Proceedings ML Family Workshop /
OCaml Users and Developers workshops, ML/OCAML 2016, Nara,
Japan, September 22-23, 2016. — 2016. — P. 1–22. 
%— Access mode:https://doi.org/10.4204/EPTCS.285.1.

\bibitem{SYB}
{\em L\"ammel R., Jones S.P.} Scrap Your Boilerplate: A Practical Design Pattern for Generic Programming // SIGPLAN Not. —
2003. — Jan. — Vol. 38, no. 3. — P. 26–37. 
%— Access mode: http://doi.acm.org/10.1145/640136.604179.

\bibitem{SYB1}
{\em L\"ammel R., Jones S.P.} Scrap More Boilerplate: Reflection, Zips, and Generalised Casts // Proceedings of the Ninth ACM
SIGPLAN International Conference on Functional Programming. —
ICFP ’04. — New York, NY, USA : ACM, 2004. — P. 244–255. 
%— Ac-cess mode: http://doi.acm.org/10.1145/1016850.1016883.

\bibitem{SYB2}
{\em L\"ammel R., Jones S. P.} Scrap Your Boilerplate with Class:
Extensible Generic Functions // SIGPLAN Not. — 2005. — Sep. —
Vol. 40, no. 9. — P. 204–215. %— Access mode: http://doi.acm.org/10.1145/1090189.1086391.

\bibitem{Bananas}
{\em Meijer E., Fokkinga M., Paterson R.} Functional Programming with Bananas, Lenses, Envelopes and Barbed Wire. — Springer-Verlag, 1991. — P. 124–144.

\bibitem{ObjectAlgebras}
{\em Oliveira B. C. d. S., Cook W.R.} Extensibility for the
Masses: Practical Extensibility with Object Algebras // Proceedings of the 26th European Conference on Object-Oriented Programming. — ECOOP’12. — Berlin, Heidelberg : Springer-Verlag,
2012. — P. 2–27.

\bibitem{Visitors}
{\em Pottier F.} Visitors Unchained // Proc. ACM Program.
Lang. — 2017. — Aug. — Vol. 1, no. ICFP. — P. 28:1–28:28. 
%— Access mode: http://doi.acm.org/10.1145/3110272.

\bibitem{ObjectAlgebrasAttribute}
{\em Tillmann R., Brachth\"auser J.I., Ostermann K. } From Object Algebras to Attribute Grammars //
 SIGPLAN Not. — 2014. — Oct. — Vol. 49, no. 10. — P. 377–395. 
% Access mode: http://doi.acm.org/10.1145/2714064.2660237.

\bibitem{ObjectAlgebrasSYB}
{\em Zhang H., Chu Z.,  Oliveira B. C.d. S., van der Storm T.}
Scrap Your Boilerplate With Object Algebras  // Proceedings of the Object-oriented Programming, Systems, Languages, and
 Applications (OOPSLA, 2015). — New York, United States, 2015. %—
% Access mode: https://hal.inria.fr/hal-01261477.

\bibitem{ALaCarte}
{\em Swierstra W.} Data Types \`a La Carte // J. Funct. Program. —
 2008. — Jul. — Vol. 18, no. 4. — P. 423–436.
% Access mode: http: //dx.doi.org/10.1017/S0956796808006758.

\bibitem{AGSwierstra}
{\em Viera M., Swierstra S. D., Swierstra W.} Attribute
 Grammars Fly First-class: How to Do Aspect Oriented 
 Program\-ming in Haskell // Proceedings of the 14th ACM SIGPLAN 
 In\-ternational Conference on Functional Programming. — ICFP ’09. —
 New York, NY, USA : ACM, 2009. — P. 245–256. 
% — Access mode: http://doi.acm.org/10.1145/1596550.1596586.

\bibitem{ExpressionProblem}
{\em Wadler P.} The Expression Problem. — 1998. — Dec.
 
\bibitem{TypeClasses}
{\em Wadler P., Blott S.} How to Make Ad-hoc Polymorphism Less Ad
 Hoc // Proceedings of the 16th ACM SIGPLAN-SIGACT Symposium on Principles of Programming Languages. — POPL ’89. — New
 York, NY, USA : ACM, 1989. — P. 60–76. 
% — Access mode: http: //doi.acm.org/10.1145/75277.75283.

 \bibitem{ModularImplicits}
{\em White L., Bour F., Yallop J.} Modular implicits // Electronic Proceedings in Theoretical Computer Science. — 2015. — 12. —
 Vol. 198.
 
 \bibitem{Yallop}
{\em Yallop J.} Practical Generic Programming in OCaml // Proceedings of the 2007 Workshop on Workshop on ML. — ML ’07. —
 New York, NY, USA : ACM, 2007. — P. 83–94. 

\bibitem{Staged} 
{\em  Yallop J.} Staged Generic Programming // Proc. ACM Program. Lang. — 2017. — Aug. — Vol. 1, no. ICFP. — P. 29:1–29:29. 
% — Access mode: http://doi.acm.org/10.1145/3110273.

\bibitem{GenericOCaml} 
{\em  Balestrieri F., Mauny M.} Proceedings ML Family Workshop / OCaml Users and Developers
workshops, Nara, Japan, September 22-23, 2016 / Ed. by Kenichi Asai,
Mark Shinwell. — Vol. 285 of Electronic Proceedings in Theoretical
Computer Science. — Open Publishing Association, 2018. — P. 59–100.

% https://dl.acm.org/doi/proceedings/10.1145/317636
\bibitem{modules-vs-objects} 
{\em       Leroy X.} 
Objects, classes and modules in Objective Caml / Proceedings of International Conference on Functional Programming, Paris /     Association for Computing Machinery, 1999.

\bibitem{irregular} 
{\em   Bird R.,  Meertens L.} 
 Nested datatypes.  /  In Mathematics of Program Construction
(MPC), volume 1422 of Lecture Notes in Computer Science, pages 52–67. Springer, 1998.


\bibitem{camlp5} 
\camlpfive{}. --- \url{https://camlp5.github.io}.
 
\bibitem{PPXLib} 
\textsc{ppxlib}. --- \url{https://github.com/ocaml-ppx/ppxlib}.

\bibitem{ppxderiving} 
ppx\_deriving. --- \url{https://github.com/ocaml-ppx/ppx\_deriving}

\bibitem{derivingMorphism} 
ppx\_deriving\_morphism. --- \url{https://github.com/ocaml-ppx/ppx\_deriving\_morphism}

\bibitem{dotNetSG}
.NET source Generators. --- \url{https://github.com/dotnet/roslyn/blob/master/docs/features/source-generators.md}


\bibitem{cardelli}
{\em Cardelli L., Wegner P.} On Understanding Types,
Data Abstraction, and Polymorphism



\bibitem{GADT}
{\em Dimitrios Vytiniotis Stephanie Weirich Simon Peyton Jones } /
.NET source Generators. Simple unification-based type inference for GADTs -- 
% https://www.microsoft.com/en-us/research/publication/simple-unification-based-type-inference-for-gadts/?from=http%3A%2F%2Fresearch.microsoft.com%2F~simonpj%2Fpapers%2Fgadt%2Findex.htm


\begin{comment}
\bibitem{AZ97}
{\em Абрамов С.А., Зима Е.В.} Семинар по компьютерной алгебре на
факультете вычислительной математики и кибернетики МГУ в 1995--1996 г.
// Программирование, 1997,
No 1. С. 75--77.

\bibitem{AZ98}
{\em Абрамов С.А., Зима Е.В.} Научно-ис\-сле\-до\-вательский семинар
``Компьютерная алгебра'' в 1996--1997 г.
// Программирование, 1998,
No 1. С. 69--72.

\bibitem{AR99}
{\em Абрамов С.А., Ростовцев В.А.} Семинар по компьютерной алгебре в
1997--1998 г.  // Программирование, 1998, No 6. С. 3--7.

\bibitem{AKR00}
{\em Абрамов С.А., Крюков А.П., Ростовцев В.А.} Семинар по компьютерной
алгебре в
1998--1999 г.  // Программирование, 2000, No 1. С. 8--12.

\bibitem{AKR01}
{\em Абрамов С.А., Крюков А.П., Ростовцев В.А.} Семинар по компьютерной
алгебре
в 1999--2000 г.  // Программирование, 2001, No 1. С. 3--7.

\bibitem{AKR02}
{\em Абрамов С.А., Крюков А.П., Ростовцев В.А.} Семинар по компьютерной
алгебре в 2000--2001 г.  // Программирование, 2002, No 2. С. 6--9.

\bibitem{AKR03}
{\em Абрамов~С.А., Крюков~А.П., Ростовцев~В.А.} Семинар по компьютерной
алгебре в 2001--2002 г. // Программирование, 2003, No 2. С. 3--7.
\bibitem{AER04}
{\em Абрамов~С.А., Еднерал~В.Ф., Ростовцев~В.А.} Семинар по
компьютерной алгебре в 2002--2003~г.  // Программирование, 2004, No 2.
С. 3--7.
\bibitem{ABRE05}
{\em Абрамов~С.А., Боголюбская~А.А., Ростовцев~В.А., Еднерал~В.Ф.} Семинар по
компьютерной алгебре в 2003--2004 г.  // Программирование, 2005, No 2.
С. 3--9.
\bibitem{ABRE06}
{\em Абрамов~С.А., Боголюбская~А.А., Ростовцев~В.А., Еднерал~В.Ф.} Семинар по
компьютерной алгебре в 2004--2005 г.  // Программирование, 2006, No 2.
С. 3--7.
\bibitem{ABRE07}
{\em Абрамов~С.А., Боголюбская~А.А., Ростовцев~В.А., Еднерал~В.Ф.} Семинар по
компьютерной алгебре в 2005--2006 г.  // Программирование, 2007, No 2.
С. 3--8.
\bibitem{ABRE08}
{\em Абрамов~С.А., Боголюбская~А.А., Ростовцев~В.А., Еднерал~В.Ф.} Семинар по
компьютерной алгебре в 2006--2007 г.  // Программирование, 2008, No 2.
С. 3--8.
\bibitem{ABRE09}
{\em Абрамов~С.А., Боголюбская~А.А., Ростовцев~В.А., Еднерал~В.Ф.} Семинар по
компьютерной алгебре в 2007--2008 г.  // Программирование, 2009, No 2.
С. 3--9.
\newpage
\bibitem{mmcp09}
``Mathematical Modeling and Computational Physics (CAAP'2009)''. Book of abstracts of the internationl conference. Dubna, July 7-11, 2009.
Dubna, 2009.
\bibitem{ABRE10}
{\em Абрамов~С.А., Боголюбская~А.А., Ростовцев~В.А., Еднерал~В.Ф.} Семинар по
компьютерной алгебре в 2008-2009 г.  // Программирование, 2010, No 2. С. 3--8.
\bibitem{ABER11}
{\em Абрамов~С.А., Боголюбская~А.А., Еднерал~В.Ф., Ростовцев~В.А.} Семинар по
компьютерной алгебре в 2009-2010 г. // Программирование, 2011, No 2. С. 3--8.
\bibitem{ABR12}
{\em Абрамов~С.А., Боголюбская~А.А.,  Ростовцев~В.А.} Семинар по
компьютерной алгебре в 2010-2011 г.  // Программирование, 2012, No 2. С. 3--10.

%
\end{comment}
\end{thebibliography}
