\documentclass
  [ a4paper        % (Predefined, but who knows...)
  , draft,         % Show bad things.
  , 12pt           % Font size.
  , pagesize,      % Writes the paper size at special areas in DVI or
                   % PDF file. Recommended for use.
  , parskip=half   % Paragraphs: noindent + gap.
  , numbers=enddot % Pointed numbers.
  , BCOR=5mm       % Binding size correction.
  , submission
  , copyright
  , creativecommons
  ]{eptcs}
\providecommand{\event}{ML 2018}  % Name of the event you are submitting to
% \usepackage{breakurl}             % Not needed if you use pdflatex only.
\usepackage{underscore}           % Only needed if you use pdflatex.

\usepackage{marginnote}


\usepackage[margin=1cm]{geometry}

\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{indentfirst}
\usepackage{verbatim}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{url}
\usepackage{stmaryrd}
\usepackage{xspace}
\usepackage{comment}
\usepackage{wrapfig}
\usepackage[caption=false]{subfig}
\usepackage{placeins}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{soul}
\usepackage{csquotes}
\usepackage{inconsolata}

\usepackage{polyglossia}   % Babel replacement for XeTeX
  \setdefaultlanguage[spelling=modern]{russian}
  \setotherlanguage{english}
\usepackage{fontspec}    % Provides an automatic and unified interface 
                         % for loading fonts.
\usepackage{xunicode}    % Generate Unicode chars from accented glyphs.
\usepackage{xltxtra}     % "Extras" for LaTeX users of XeTeX.
\usepackage{xecyr}       % Help with Russian.

%% Fonts
\defaultfontfeatures{Mapping=tex-text}
\setmainfont{CMU Serif}
\setsansfont{CMU Sans Serif}
\setmonofont{CMU Typewriter Text}

\usepackage[final]{listings}

\lstdefinelanguage{ocaml}{
keywords={@type, function, fun, let, in, match, with, when, class, type,
nonrec, object, method, of, rec, repeat, until, while, not, do, done, as, val, inherit, and,
new, module, sig, deriving, datatype, struct, if, then, else, open, private, virtual, include, success, failure,
lazy, assert, true, false, end},
sensitive=true,
commentstyle=\small\itshape\ttfamily,
keywordstyle=\ttfamily\bfseries, %\underbar,
identifierstyle=\ttfamily,
basewidth={0.5em,0.5em},
columns=fixed,
fontadjust=true,
literate={->}{{$\to$}}3 {===}{{$\equiv$}}1 {=/=}{{$\not\equiv$}}1 {|>}{{$\triangleright$}}3 {\\/}{{$\vee$}}2 {/\\}{{$\wedge$}}2 {>=}{{$\ge$}}1 {<=}{{$\le$}} 1,
morecomment=[s]{(*}{*)}
}

\lstset{
mathescape=true,
%basicstyle=\small,
identifierstyle=\ttfamily,
keywordstyle=\bfseries,
commentstyle=\scriptsize\rmfamily,
basewidth={0.5em,0.5em},
fontadjust=true,
language=ocaml
}

\newcommand{\cd}[1]{\texttt{#1}}
\newcommand{\inbr}[1]{\left<#1\right>}
%\pagestyle{plain}
\sloppy

\title{Generic Programming with Combinators and Objects йцукен\thanks{This work was partially supported by the grant 18-01-00380 from the Russian Foundation for Basic Research.}}

\author{Dmitry Kosarev
  \institute{St. Petersburg State University\\
    JetBrains Research \\
    St. Petersburg, Russia}
\email{Dmitrii.Kosarev@protonmail.ch}
\and
Dmitry Boulytchev
\institute{St. Petersburg State University\\
  JetBrains Research \\
  St. Petersburg, Russia}
\email{dboulytchev@math.spbu.ru}
}

\def\titlerunning{Generic Programming with Combinators and Objects}
\def\authorrunning{D.Kosarev, D.Boulytchev}

\begin{document}
\maketitle

\begin{abstract}
  We present a generic programming framework for \textsc{OCaml} which makes it possible to implement extensible
  transformations for a large scale of type definitions. Our framework makes use of object-oriented features
  of \textsc{OCaml}, utilising late binding to override the default behaviour of generated transformations. The
  support for polymorphic variant types complements the ability to describe composable data types with the
  ability to implement composable transformations.
  
  В данной работе представлен подход для языка программирования \textsc{OCaml}, который позволяет реализовывать расширяемые трансформации для различных видов определений типов. Этот подход
  использует объектно-ориентированные возможности \textsc{OCaml},
  а именно позднее связывание, чтобы изменять поведение по-умолчанию
  автоматически сгенерированных трансформаций. Поддержка полиморфных вариантных типов позволяет композиционально описывать  типы данных
  с возможностью реализовать композициональные преобразования.
\end{abstract}

\input{intro.tex}
% \input{exposition.tex}
% \input{impl.tex}
% \input{examples.tex}
\input{related.tex}
% \input{conclusion.tex}

\nocite{*}
\bibliographystyle{eptcs}
\bibliography{vkr}
\end{document}
